---
title: 'MCCL Recombination Model Simulation: First Run'
author: "Grace Rhodes"
date: "7/20/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(sfsmisc)
source("reading_data.R", local = knitr::knit_global() )
source("ancestor_general.R", local = knitr::knit_global() )
source("ancestor_L3_bitwise.R", local = knitr::knit_global() )
source("onewise_marginal.R", local = knitr::knit_global() )
source("pairwise-marginal.R", local = knitr::knit_global() )
source("threewise_marginal.R", local = knitr::knit_global() )
source("fourwise_marginal.R", local = knitr::knit_global() )
```

For first test run on a simulation, use the following settings

- Data: HapMap YRI population TRIOS for chromosome 1 (200 haplotypes)

- Number of Descendants Generated: $n = 50$

- Number of Replications: $N = 100$

- Recombination Probability: $q = 0.01$

- Sequence Length: $L = 100$ *change to L=20 because of computer storage issue*

Compute the following performance measures:

- Computation time using $proc.time()$

- Bias for parameter $\pi_{1,2,3,4}(0,0,0,0)$

- Standard deviation for parameter $\pi_{1,2,3,4}(0,0,0,0)$

###STEP ONE: Read in the data to generate the simulated ancestor

Raw data:
```{r}
head(yri_trio_1)
```

Data converted to binary sequences:

**conversion done in R script "reading_data.R"
```{r}
head(hapmap_binary)
```

###STEP TWO: Simulate the ancestor 

Using function "ancestor()" from script "ancestor_general.R"

```{r}
ancestor_sim1 <- ancestor(L=20, hapmap_data = hapmap_binary)
head(ancestor_sim1)
```

Based on this ancestor distribution, we take the true parameter of interest to be:
$$\pi_{1,2,\ldots , 20}(0,0, \ldots , 0 = 0.025.$$

For the bias, calculation use equation:
$$\hat{\pi}_{1,2,\ldots , 20}(0,0, \ldots , 0) = \frac{\hat{\pi}_{1,2,3,4}(0,0,0,0) \hat{\pi}_{2,3,4,5}(0,0,0,0) \ldots \hat{\pi}_{17,18,19,20}}{\hat{\pi}_{2,3,4}(0,0,0) \ldots \hat{\pi}_{17,18,19}(0,0,0)}$$

```{r}
# initialize matrix to store bias and SD
simulation_results <- matrix(NA, nrow = 100, ncol = 1)
colnames(simulation_results) <- c("estimate")

comp_time1 <- proc.time()
# 100 REPLICATIONS
for (i in 1:100){
  # find descendant sample using index as the seed
  descend_sample <- descendent_sample(L=20, q=0.01, n=100, seed = i, hapmap = hapmap_binary)
  
  # find threewise estimate
  threewise_estimates <- estimates_m2(L=20, q=0.01, n=100, descend=descend_sample)
  
  # find fourwise estimate
  fourwise_estimates <- estimates_m3(L=20, q=0.01, n=100, d=descend_sample)
  
  # calculate estimate of parameter of interest
  para <- (prod(fourwise_estimates[1,]) / prod(threewise_estimates[1, 2:17]))
  
  # append estimate for this replication into the matrix
  simulation_results[i,] <- para
}
comp_timefinal <- proc.time() - comp_time1
```

Calculate the bias:

```{r}
bias <- mean(simulation_results[,1]) - ancestor_sim1[1,1]
bias
```

Calculate the standard deviation:

```{r}
stand_dev <- sd(simulation_results[,1])
stand_dev
```

Computation time:

```{r}
comp_timefinal
```

Tentative interpretation:

Based on this simulation, the estimator yielded an estimate with relatively low bias (0.002978265) and small standard deviation (0.009381513). However, even for this small sequence length (L=20) the computation time was sizable (3504.96 milliseconds)
